---
title: "Exploratory Data Analysis"
author: "Areeka Aijaz"
date: "1/13/2021"
output: html_document
---

```{r including external files, echo=FALSE, message=FALSE}
library(dplyr)
library(ggplot2)

setwd("E:\\FYP\\FYP-1 (Part 2)\\Implementation")
source("functions.R")

```


```{r, echo=FALSE}

# Read data
semester_data <- read.csv("E:\\FYP\\FYP-1 (Part 2)\\Datasets\\Cleaned_Semester_Data.csv", stringsAsFactors = FALSE, na.strings=c("","NA"))
student_data <- read.csv("E:\\FYP\\FYP-1 (Part 2)\\Datasets\\Cleaned_Student_Data.csv", na.strings=c("","NA"))
```

```{r, echo=FALSE}

data <- merge(semester_data, student_data, by = "STUDENT_ID")

data <- data %>% filter(GENDER != "-")

summary(data)
str(data)

```

## Exploratory Data Analysis

## Visualizing Whole Data

### Total Students

```{r, echo=FALSE}
print(paste("Total Students: ", nrow(data)))
```

### Missing Values in Dataset

```{r, echo=FALSE}
colSums(is.na(data))
```

### Total Students in Each Campus

```{r, echo=FALSE}
print(paste("Total Campuses: ", length(unique(data$CAMPUS))))
campus_detail <- data %>% group_by(CAMPUS) %>% summarise(Student_Count = n()) 
knitr::kable(campus_detail)
data %>% ggplot(aes(CAMPUS, fill = CAMPUS)) + geom_bar() + ylab("STUDENT") + theme_bw()
```

### Total Students enrolled in Each Degree Program

```{r, echo=FALSE}
print(paste("Total Degree Programs: ", length(unique(data$PROG_CODE))))
prog_detail <- data %>% group_by(PROG_CODE) %>% summarise(Student_Count = n()) 
knitr::kable(prog_detail)
data %>% ggplot(aes(PROG_CODE, fill = PROG_CODE)) + geom_bar() + ylab("STUDENT") + theme_bw() + theme(axis.text.x = element_text(size=6))
```

### Programs offered in Each Campus

```{r, echo=FALSE}
data %>% ggplot(aes(CAMPUS, fill = PROG_CODE)) + geom_bar(position = "dodge") + ggtitle("Programs offered in Each Campus") + ylab("STUDENT") + theme_bw() + theme(axis.text.x = element_text(size=6))
```

### Total Male & Female Students

```{r, echo=FALSE}
gender_detail <- data %>% group_by(GENDER) %>% summarise(Student_Count = n()) 
knitr::kable(gender_detail)
data %>% ggplot(aes(GENDER, fill = GENDER)) + geom_bar() + ylab("STUDENT") + theme_bw()
```

### No. of Male & Female Students in Each Campus

```{r, echo=FALSE}
data %>% ggplot(aes(CAMPUS, fill = GENDER)) + geom_bar(position = "dodge") + ggtitle("No. of Male & Female Students in Each Campus") + ylab("STUDENT") + theme_bw()
```

### Status of Students

```{r, echo=FALSE}
print(paste("Unique Statuses: ", length(unique(data$STATUS))))
status_detail <- data %>% group_by(STATUS) %>% summarise(Student_Count = n()) 
knitr::kable(status_detail)
data %>% ggplot(aes(STATUS, fill = STATUS)) + geom_bar() + ylab("STUDENT") + theme_bw()
```

### Status of Students for Each Campus

```{r, echo=FALSE}
data %>% ggplot(aes(CAMPUS, fill = STATUS)) + geom_bar(position = "dodge") + ggtitle("Status of Students for Each Campus") + ylab("STUDENT") + theme_bw()
```

### Status of Students wrt their Graduation Year

```{r, echo=FALSE}

data %>% filter(grepl("Fall", LAST_SEM), !grepl("Current", STATUS)) %>% ggplot(aes(STATUS, fill = STATUS)) + geom_bar() + ylab("STUDENT") + ggtitle("Status of Students - Fall Semesters") + theme_bw() + facet_wrap(~LAST_SEM, ncol = 5) + theme(axis.text.x = element_text(size=8, angle=90, hjust=.5, vjust=.5))

data %>% filter(grepl("Spring", LAST_SEM), !grepl("Current", STATUS)) %>% ggplot(aes(STATUS, fill = STATUS)) + geom_bar() + ylab("STUDENT") + ggtitle("Status of Students - Spring Semesters") + theme_bw() + facet_wrap(~LAST_SEM, ncol = 5) + theme(axis.text.x = element_text(size=8, angle=90, hjust=.5, vjust=.5))

data %>% filter(grepl("Summer", LAST_SEM), !grepl("Current", STATUS)) %>% ggplot(aes(STATUS, fill = STATUS)) + geom_bar() + ylab("STUDENT") + ggtitle("Status of Students - Summer Semesters") + theme_bw() + facet_wrap(~LAST_SEM, ncol = 5) + theme(axis.text.x = element_text(size=8, angle=90, hjust=.5, vjust=.5))

```

### Students from Different Cities

```{r, echo=FALSE}
print(paste("Total Cities: ", length(unique(data$CITY))))
city_detail <- data %>% group_by(CITY) %>% summarise(Student_Count = n()) %>% filter(Student_Count > 50)
knitr::kable(city_detail)
print(paste("Cities after threshold: ", nrow(city_detail)))
data %>% group_by(CITY) %>% count %>% filter(n > 50) %>% ggplot(aes(x = CITY, y = n, fill = CITY)) + geom_bar(stat = "identity") + ylab("STUDENT") + ggtitle("No. of Students from Different Citites") + theme_bw() + theme(axis.text.x = element_text(size=6, angle=90, hjust=.6, vjust=.5), legend.position = "none")
```

### Students from Different Cities for Each Campus

```{r, echo=FALSE}
city_detail <- data %>% group_by(CAMPUS, CITY) %>% summarise(Student_Count = n()) %>% filter(Student_Count > 30)
knitr::kable(city_detail)
print(paste("Cities after threshold: ", nrow(city_detail)))

data %>% group_by(CAMPUS, CITY) %>% count %>% filter(n > 30) %>% ggplot(aes(x = CITY, y = n, fill = CAMPUS)) + geom_bar(stat = "identity") + ylab("STUDENT") + ggtitle("No. of Students from Different Citites for Each Campus") + theme_bw() + theme(axis.text.x = element_text(size=6, angle=90, hjust=.6, vjust=.5))

```

### Educational Background of Students (SSC / O_LEVEL)

```{r, echo=FALSE}
suppressWarnings(edu1_detail <- data %>% group_by(SECONDARY) %>% summarise(Student_Count = n())) 
knitr::kable(edu1_detail)
data %>% ggplot(aes(SECONDARY, fill = SECONDARY)) + geom_bar() + ylab("STUDENT") + theme_bw()
```

### Educational Background of Students (HSSC / A_LEVEL)

```{r, echo=FALSE}
suppressWarnings(edu2_detail <- data %>% group_by(HIGHER_SECONDARY) %>% summarise(Student_Count = n()))
knitr::kable(edu2_detail)
data %>% ggplot(aes(HIGHER_SECONDARY, fill = HIGHER_SECONDARY)) + geom_bar() + ylab("STUDENT") + theme_bw()
```

### Overall CGPA of All Campuses

```{r, echo=FALSE}

campus_detail <- data %>% group_by(CAMPUS) %>% summarise(Student_Count = n(), Min = round(min(CGPA), digits = 2), First_Quartile = round(summary(CGPA)[2], digits = 2),  Median = round(median(CGPA), digits = 2), Mean = round(mean(CGPA), digits = 2), Third_Quartile = round(summary(CGPA)[5], digits = 2), Max = round(max(CGPA), digits = 2))

knitr::kable(campus_detail)

data %>% ggplot(aes(CAMPUS, CGPA, color = CAMPUS)) + geom_boxplot() + theme(axis.text.x = element_text(size=6)) + ggtitle("Relationship between CAMPUS & CGPA") + theme_bw()

```

## Campus-wise Visualization

### KARACHI Campus

```{r, echo=FALSE}
KARACHI_data <- data %>% filter(grepl("KHI", CAMPUS))
```

### Total Students enrolled in Each Degree Program

```{r, echo=FALSE}
print(paste("Total Degree Programs offered in KARACHI Campus: ", length(unique(KARACHI_data$PROG_CODE))))
prog_detail <- KARACHI_data %>% group_by(PROG_CODE) %>% summarise(Student_Count = n()) 
knitr::kable(prog_detail)
KARACHI_data %>% ggplot(aes(PROG_CODE, fill = PROG_CODE)) + geom_bar() + ylab("STUDENT") + theme_bw() + theme(axis.text.x = element_text(size=6))
```

### Total Male & Female Students

```{r, echo=FALSE}
print(paste("Total Students enrolled in KARACHI Campus: ", nrow(KARACHI_data)))
gender_detail <- KARACHI_data %>% group_by(GENDER) %>% summarise(Student_Count = n()) 
knitr::kable(gender_detail)
KARACHI_data %>% ggplot(aes(GENDER, fill = GENDER)) + geom_bar() + ylab("STUDENT") + theme_bw()
```

### Status of Students

```{r, echo=FALSE}
print(paste("Unique Statuses: ", length(unique(KARACHI_data$STATUS))))
status_detail <- KARACHI_data %>% group_by(STATUS) %>% summarise(Student_Count = n()) 
knitr::kable(status_detail)
KARACHI_data %>% ggplot(aes(STATUS, fill = STATUS)) + geom_bar() + ylab("STUDENT") + theme_bw()
```

### Status of Students wrt their Graduation Year

```{r, echo=FALSE}

KARACHI_data %>% filter(grepl("Fall", LAST_SEM), !grepl("Current", STATUS)) %>% ggplot(aes(STATUS, fill = STATUS)) + geom_bar() + ylab("STUDENT") + ggtitle("Status of Students - Fall Semesters") + theme_bw() + facet_wrap(~LAST_SEM, ncol = 5) + theme(axis.text.x = element_text(size=8, angle=90, hjust=.5, vjust=.5))

KARACHI_data %>% filter(grepl("Spring", LAST_SEM), !grepl("Current", STATUS)) %>% ggplot(aes(STATUS, fill = STATUS)) + geom_bar() + ylab("STUDENT") + ggtitle("Status of Students - Spring Semesters") + theme_bw() + facet_wrap(~LAST_SEM, ncol = 5) + theme(axis.text.x = element_text(size=8, angle=90, hjust=.5, vjust=.5))

KARACHI_data %>% filter(grepl("Summer", LAST_SEM), !grepl("Current", STATUS)) %>% ggplot(aes(STATUS, fill = STATUS)) + geom_bar() + ylab("STUDENT") + ggtitle("Status of Students - Summer Semesters") + theme_bw() + facet_wrap(~LAST_SEM, ncol = 5) + theme(axis.text.x = element_text(size=8, angle=90, hjust=.5, vjust=.5))

```

### Students from Different Cities

```{r, echo=FALSE}
print(paste("Total Cities: ", length(unique(KARACHI_data$CITY))))
city_detail <- KARACHI_data %>% group_by(CITY) %>% summarise(Student_Count = n()) %>% filter(Student_Count > 10)
knitr::kable(city_detail)
print(paste("Cities after threshold: ", nrow(city_detail)))
KARACHI_data %>% group_by(CITY) %>% count %>% filter(n > 10) %>% ggplot(aes(x = CITY, y = n, fill = CITY)) + geom_bar(stat = "identity") + ylab("Student") + ggtitle("No. of Students from different Citites") + theme_bw() + theme(axis.text.x = element_text(size=6, angle=90, hjust=.6, vjust=.5), legend.position = "none")
```

### Educational Background of Students (SSC / O_LEVEL)

```{r, echo=FALSE}
suppressWarnings(edu1_detail <- KARACHI_data %>% group_by(SECONDARY) %>% summarise(Student_Count = n())) 
knitr::kable(edu1_detail)
KARACHI_data %>% ggplot(aes(SECONDARY, fill = SECONDARY)) + geom_bar() + ylab("STUDENT") + theme_bw()
```

### Educational Background of Students (HSSC / A_LEVEL)

```{r, echo=FALSE}
suppressWarnings(edu2_detail <- KARACHI_data %>% group_by(HIGHER_SECONDARY) %>% summarise(Student_Count = n()))
knitr::kable(edu2_detail)
KARACHI_data %>% ggplot(aes(HIGHER_SECONDARY, fill = HIGHER_SECONDARY)) + geom_bar() + ylab("STUDENT") + theme_bw()
```

### ISLAMABAD Campus

```{r, echo=FALSE}
ISLAMABAD_data <- data %>% filter(grepl("ISB", CAMPUS))
```

### Total Students enrolled in Each Degree Program

```{r, echo=FALSE}
print(paste("Total Degree Programs offered in ISLAMABAD Campus: ", length(unique(ISLAMABAD_data$PROG_CODE))))
prog_detail <- ISLAMABAD_data %>% group_by(PROG_CODE) %>% summarise(Student_Count = n()) 
knitr::kable(prog_detail)
ISLAMABAD_data %>% ggplot(aes(PROG_CODE, fill = PROG_CODE)) + geom_bar() + ylab("STUDENT") + theme_bw() + theme(axis.text.x = element_text(size=6))
```

### Total Male & Female Students

```{r, echo=FALSE}
print(paste("Total Students enrolled in ISLAMABAD Campus: ", nrow(ISLAMABAD_data)))
gender_detail <- ISLAMABAD_data %>% group_by(GENDER) %>% summarise(Student_Count = n()) 
knitr::kable(gender_detail)
ISLAMABAD_data %>% ggplot(aes(GENDER, fill = GENDER)) + geom_bar() + ylab("STUDENT") + theme_bw()
```

### Status of Students

```{r, echo=FALSE}
print(paste("Unique Statuses: ", length(unique(ISLAMABAD_data$STATUS))))
status_detail <- ISLAMABAD_data %>% group_by(STATUS) %>% summarise(Student_Count = n()) 
knitr::kable(status_detail)
ISLAMABAD_data %>% ggplot(aes(STATUS, fill = STATUS)) + geom_bar() + ylab("STUDENT") + theme_bw()
```

### Status of Students wrt their Graduation Year

```{r, echo=FALSE}

ISLAMABAD_data %>% filter(grepl("Fall", LAST_SEM), !grepl("Current", STATUS)) %>% ggplot(aes(STATUS, fill = STATUS)) + geom_bar() + ylab("STUDENT") + ggtitle("Status of Students - Fall Semesters") + theme_bw() + facet_wrap(~LAST_SEM, ncol = 5) + theme(axis.text.x = element_text(size=8, angle=90, hjust=.5, vjust=.5))

ISLAMABAD_data %>% filter(grepl("Spring", LAST_SEM), !grepl("Current", STATUS)) %>% ggplot(aes(STATUS, fill = STATUS)) + geom_bar() + ylab("STUDENT") + ggtitle("Status of Students - Spring Semesters") + theme_bw() + facet_wrap(~LAST_SEM, ncol = 5) + theme(axis.text.x = element_text(size=8, angle=90, hjust=.5, vjust=.5))

ISLAMABAD_data %>% filter(grepl("Summer", LAST_SEM), !grepl("Current", STATUS)) %>% ggplot(aes(STATUS, fill = STATUS)) + geom_bar() + ylab("STUDENT") + ggtitle("Status of Students - Summer Semesters") + theme_bw() + facet_wrap(~LAST_SEM, ncol = 5) + theme(axis.text.x = element_text(size=8, angle=90, hjust=.5, vjust=.5))

```

### Students from Different Cities

```{r, echo=FALSE}
print(paste("Total Cities: ", length(unique(ISLAMABAD_data$CITY))))
city_detail <- ISLAMABAD_data %>% group_by(CITY) %>% summarise(Student_Count = n()) %>% filter(Student_Count > 10)
knitr::kable(city_detail)
print(paste("Cities after threshold: ", nrow(city_detail)))
ISLAMABAD_data %>% group_by(CITY) %>% count %>% filter(n > 10) %>% ggplot(aes(x = CITY, y = n, fill = CITY)) + geom_bar(stat = "identity") + ylab("Student") + ggtitle("No. of Students from different Citites") + theme_bw() + theme(axis.text.x = element_text(size=6, angle=90, hjust=.6, vjust=.5), legend.position = "none")
```

### Educational Background of Students (SSC / O_LEVEL)

```{r, echo=FALSE}
suppressWarnings(edu1_detail <- ISLAMABAD_data %>% group_by(SECONDARY) %>% summarise(Student_Count = n())) 
knitr::kable(edu1_detail)
ISLAMABAD_data %>% ggplot(aes(SECONDARY, fill = SECONDARY)) + geom_bar() + ylab("STUDENT") + theme_bw()
```

### Educational Background of Students (HSSC / A_LEVEL)

```{r, echo=FALSE}
suppressWarnings(edu2_detail <- ISLAMABAD_data %>% group_by(HIGHER_SECONDARY) %>% summarise(Student_Count = n()))
knitr::kable(edu2_detail)
ISLAMABAD_data %>% ggplot(aes(HIGHER_SECONDARY, fill = HIGHER_SECONDARY)) + geom_bar() + ylab("STUDENT") + theme_bw()
```

### LAHORE Campus

```{r, echo=FALSE}
LAHORE_data <- data %>% filter(grepl("LHR", CAMPUS))
```

### Total Students enrolled in Each Degree Program

```{r, echo=FALSE}
print(paste("Total Degree Programs offered in LAHORE Campus: ", length(unique(LAHORE_data$PROG_CODE))))
prog_detail <- LAHORE_data %>% group_by(PROG_CODE) %>% summarise(Student_Count = n()) 
knitr::kable(prog_detail)
LAHORE_data %>% ggplot(aes(PROG_CODE, fill = PROG_CODE)) + geom_bar() + ylab("STUDENT") + theme_bw() + theme(axis.text.x = element_text(size=6))
```

### Total Male & Female Students

```{r, echo=FALSE}
print(paste("Total Students enrolled in LAHORE Campus: ", nrow(LAHORE_data)))
gender_detail <- LAHORE_data %>% group_by(GENDER) %>% summarise(Student_Count = n()) 
knitr::kable(gender_detail)
LAHORE_data %>% ggplot(aes(GENDER, fill = GENDER)) + geom_bar() + ylab("STUDENT") + theme_bw()
```

### Status of Students

```{r, echo=FALSE}
print(paste("Unique Statuses: ", length(unique(LAHORE_data$STATUS))))
status_detail <- LAHORE_data %>% group_by(STATUS) %>% summarise(Student_Count = n()) 
knitr::kable(status_detail)
LAHORE_data %>% ggplot(aes(STATUS, fill = STATUS)) + geom_bar() + ylab("STUDENT") + theme_bw()
```

### Status of Students wrt their Graduation Year

```{r, echo=FALSE}

LAHORE_data %>% filter(grepl("Fall", LAST_SEM), !grepl("Current", STATUS)) %>% ggplot(aes(STATUS, fill = STATUS)) + geom_bar() + ylab("STUDENT") + ggtitle("Status of Students - Fall Semesters") + theme_bw() + facet_wrap(~LAST_SEM, ncol = 5) + theme(axis.text.x = element_text(size=8, angle=90, hjust=.5, vjust=.5))

LAHORE_data %>% filter(grepl("Spring", LAST_SEM), !grepl("Current", STATUS)) %>% ggplot(aes(STATUS, fill = STATUS)) + geom_bar() + ylab("STUDENT") + ggtitle("Status of Students - Spring Semesters") + theme_bw() + facet_wrap(~LAST_SEM, ncol = 5) + theme(axis.text.x = element_text(size=8, angle=90, hjust=.5, vjust=.5))

LAHORE_data %>% filter(grepl("Summer", LAST_SEM), !grepl("Current", STATUS)) %>% ggplot(aes(STATUS, fill = STATUS)) + geom_bar() + ylab("STUDENT") + ggtitle("Status of Students - Summer Semesters") + theme_bw() + facet_wrap(~LAST_SEM, ncol = 5) + theme(axis.text.x = element_text(size=8, angle=90, hjust=.5, vjust=.5))

```

### Students from Different Cities

```{r, echo=FALSE}
print(paste("Total Cities: ", length(unique(LAHORE_data$CITY))))
city_detail <- LAHORE_data %>% group_by(CITY) %>% summarise(Student_Count = n()) %>% filter(Student_Count > 10)
knitr::kable(city_detail)
print(paste("Cities after threshold: ", nrow(city_detail)))
LAHORE_data %>% group_by(CITY) %>% count %>% filter(n > 10) %>% ggplot(aes(x = CITY, y = n, fill = CITY)) + geom_bar(stat = "identity") + ylab("Student") + ggtitle("No. of Students from different Citites") + theme_bw() + theme(axis.text.x = element_text(size=6, angle=90, hjust=.6, vjust=.5), legend.position = "none")
```

### Educational Background of Students (SSC / O_LEVEL)

```{r, echo=FALSE}
suppressWarnings(edu1_detail <- LAHORE_data %>% group_by(SECONDARY) %>% summarise(Student_Count = n())) 
knitr::kable(edu1_detail)
LAHORE_data %>% ggplot(aes(SECONDARY, fill = SECONDARY)) + geom_bar() + ylab("STUDENT") + theme_bw()
```

### Educational Background of Students (HSSC / A_LEVEL)

```{r, echo=FALSE}
suppressWarnings(edu2_detail <- LAHORE_data %>% group_by(HIGHER_SECONDARY) %>% summarise(Student_Count = n()))
knitr::kable(edu2_detail)
LAHORE_data %>% ggplot(aes(HIGHER_SECONDARY, fill = HIGHER_SECONDARY)) + geom_bar() + ylab("STUDENT") + theme_bw()
```

### PESHAWAR Campus

```{r, echo=FALSE}
PESHAWAR_data <- data %>% filter(grepl("PWR", CAMPUS))
```

### Total Students enrolled in Each Degree Program

```{r, echo=FALSE}
print(paste("Total Degree Programs offered in PESHAWAR Campus: ", length(unique(PESHAWAR_data$PROG_CODE))))
prog_detail <- PESHAWAR_data %>% group_by(PROG_CODE) %>% summarise(Student_Count = n()) 
knitr::kable(prog_detail)
PESHAWAR_data %>% ggplot(aes(PROG_CODE, fill = PROG_CODE)) + geom_bar() + ylab("STUDENT") + theme_bw() + theme(axis.text.x = element_text(size=6))
```

### Total Male & Female Students

```{r, echo=FALSE}
print(paste("Total Students enrolled in PESHAWAR Campus: ", nrow(PESHAWAR_data)))
gender_detail <- PESHAWAR_data %>% group_by(GENDER) %>% summarise(Student_Count = n()) 
knitr::kable(gender_detail)
PESHAWAR_data %>% ggplot(aes(GENDER, fill = GENDER)) + geom_bar() + ylab("STUDENT") + theme_bw()
```

### Status of Students

```{r, echo=FALSE}
print(paste("Unique Statuses: ", length(unique(PESHAWAR_data$STATUS))))
status_detail <- PESHAWAR_data %>% group_by(STATUS) %>% summarise(Student_Count = n()) 
knitr::kable(status_detail)
PESHAWAR_data %>% ggplot(aes(STATUS, fill = STATUS)) + geom_bar() + ylab("STUDENT") + theme_bw()
```

### Status of Students wrt their Graduation Year

```{r, echo=FALSE}

PESHAWAR_data %>% filter(grepl("Fall", LAST_SEM), !grepl("Current", STATUS)) %>% ggplot(aes(STATUS, fill = STATUS)) + geom_bar() + ylab("STUDENT") + ggtitle("Status of Students - Fall Semesters") + theme_bw() + facet_wrap(~LAST_SEM, ncol = 5) + theme(axis.text.x = element_text(size=8, angle=90, hjust=.5, vjust=.5))

PESHAWAR_data %>% filter(grepl("Spring", LAST_SEM), !grepl("Current", STATUS)) %>% ggplot(aes(STATUS, fill = STATUS)) + geom_bar() + ylab("STUDENT") + ggtitle("Status of Students - Spring Semesters") + theme_bw() + facet_wrap(~LAST_SEM, ncol = 5) + theme(axis.text.x = element_text(size=8, angle=90, hjust=.5, vjust=.5))

PESHAWAR_data %>% filter(grepl("Summer", LAST_SEM), !grepl("Current", STATUS)) %>% ggplot(aes(STATUS, fill = STATUS)) + geom_bar() + ylab("STUDENT") + ggtitle("Status of Students - Summer Semesters") + theme_bw() + facet_wrap(~LAST_SEM, ncol = 5) + theme(axis.text.x = element_text(size=8, angle=90, hjust=.5, vjust=.5))

```

### Students from Different Cities

```{r, echo=FALSE}
print(paste("Total Cities: ", length(unique(PESHAWAR_data$CITY))))
city_detail <- PESHAWAR_data %>% group_by(CITY) %>% summarise(Student_Count = n()) %>% filter(Student_Count > 10)
knitr::kable(city_detail)
print(paste("Cities after threshold: ", nrow(city_detail)))
PESHAWAR_data %>% group_by(CITY) %>% count %>% filter(n > 10) %>% ggplot(aes(x = CITY, y = n, fill = CITY)) + geom_bar(stat = "identity") + ylab("Student") + ggtitle("No. of Students from different Citites") + theme_bw() + theme(axis.text.x = element_text(size=6, angle=90, hjust=.6, vjust=.5), legend.position = "none")
```

### Educational Background of Students (SSC / O_LEVEL)
```{r, echo=FALSE}
suppressWarnings(edu1_detail <- PESHAWAR_data %>% group_by(SECONDARY) %>% summarise(Student_Count = n())) 
knitr::kable(edu1_detail)
PESHAWAR_data %>% ggplot(aes(SECONDARY, fill = SECONDARY)) + geom_bar() + ylab("STUDENT") + theme_bw()
```

### Educational Background of Students (HSSC / A_LEVEL)
```{r, echo=FALSE}
suppressWarnings(edu2_detail <- PESHAWAR_data %>% group_by(HIGHER_SECONDARY) %>% summarise(Student_Count = n()))
knitr::kable(edu2_detail)
PESHAWAR_data %>% ggplot(aes(HIGHER_SECONDARY, fill = HIGHER_SECONDARY)) + geom_bar() + ylab("STUDENT") + theme_bw()
```

### FAISALABAD Campus

```{r, echo=FALSE}
FAISLABAD_data <- data %>% filter(grepl("FSD", CAMPUS))
```

### Total Students enrolled in Each Degree Program

```{r, echo=FALSE}
print(paste("Total Degree Programs offered in FAISALABAD Campus: ", length(unique(FAISLABAD_data$PROG_CODE))))
prog_detail <- FAISLABAD_data %>% group_by(PROG_CODE) %>% summarise(Student_Count = n()) 
knitr::kable(prog_detail)
FAISLABAD_data %>% ggplot(aes(PROG_CODE, fill = PROG_CODE)) + geom_bar() + ylab("STUDENT") + theme_bw() + theme(axis.text.x = element_text(size=6)) 
```

### Total Male & Female Students

```{r, echo=FALSE}
print(paste("Total Students enrolled in FAISALABAD Campus: ", nrow(FAISLABAD_data)))
gender_detail <- FAISLABAD_data %>% group_by(GENDER) %>% summarise(Student_Count = n()) 
knitr::kable(gender_detail)
FAISLABAD_data %>% ggplot(aes(GENDER, fill = GENDER)) + geom_bar() + ylab("STUDENT") + theme_bw()
```

### Status of Students

```{r, echo=FALSE}
print(paste("Unique Statuses: ", length(unique(FAISLABAD_data$STATUS))))
status_detail <- FAISLABAD_data %>% group_by(STATUS) %>% summarise(Student_Count = n()) 
knitr::kable(status_detail)
FAISLABAD_data %>% ggplot(aes(STATUS, fill = STATUS)) + geom_bar() + ylab("STUDENT") + theme_bw()
```

### Status of Students wrt their Graduation Year

```{r, echo=FALSE}

FAISLABAD_data %>% filter(grepl("Fall", LAST_SEM), !grepl("Current", STATUS)) %>% ggplot(aes(STATUS, fill = STATUS)) + geom_bar() + ylab("STUDENT") + ggtitle("Status of Students - Fall Semesters") + theme_bw() + facet_wrap(~LAST_SEM, ncol = 5) + theme(axis.text.x = element_text(size=8, angle=90, hjust=.5, vjust=.5))

FAISLABAD_data %>% filter(grepl("Spring", LAST_SEM), !grepl("Current", STATUS)) %>% ggplot(aes(STATUS, fill = STATUS)) + geom_bar() + ylab("STUDENT") + ggtitle("Status of Students - Spring Semesters") + theme_bw() + facet_wrap(~LAST_SEM, ncol = 5) + theme(axis.text.x = element_text(size=8, angle=90, hjust=.5, vjust=.5))

FAISLABAD_data %>% filter(grepl("Summer", LAST_SEM), !grepl("Current", STATUS)) %>% ggplot(aes(STATUS, fill = STATUS)) + geom_bar() + ylab("STUDENT") + ggtitle("Status of Students - Summer Semesters") + theme_bw() + facet_wrap(~LAST_SEM, ncol = 5) + theme(axis.text.x = element_text(size=8, angle=90, hjust=.5, vjust=.5))

```

### Students from Different Cities

```{r, echo=FALSE}
print(paste("Total Cities: ", length(unique(FAISLABAD_data$CITY))))
city_detail <- FAISLABAD_data %>% group_by(CITY) %>% summarise(Student_Count = n()) %>% filter(Student_Count > 10)
knitr::kable(city_detail)
print(paste("Cities after threshold: ", nrow(city_detail)))
FAISLABAD_data %>% group_by(CITY) %>% count %>% filter(n > 10) %>% ggplot(aes(x = CITY, y = n, fill = CITY)) + geom_bar(stat = "identity") + ylab("Student") + ggtitle("No. of Students from different Citites") + theme_bw() + theme(axis.text.x = element_text(size=6, angle=90, hjust=.6, vjust=.5), legend.position = "none")
```

### Educational Background of Students (SSC / O_LEVEL)
```{r, echo=FALSE}
suppressWarnings(edu1_detail <- FAISLABAD_data %>% group_by(SECONDARY) %>% summarise(Student_Count = n())) 
knitr::kable(edu1_detail)
FAISLABAD_data %>% ggplot(aes(SECONDARY, fill = SECONDARY)) + geom_bar() + ylab("STUDENT") + theme_bw()
```

### Educational Background of Students (HSSC / A_LEVEL)
```{r, echo=FALSE}
suppressWarnings(edu2_detail <- FAISLABAD_data %>% group_by(HIGHER_SECONDARY) %>% summarise(Student_Count = n()))
knitr::kable(edu2_detail)
FAISLABAD_data %>% ggplot(aes(HIGHER_SECONDARY, fill = HIGHER_SECONDARY)) + geom_bar() + ylab("STUDENT") + theme_bw()
```